---
pagetitle: "Your Headline Here"
output:
  html_document:
    theme: null
    highlight: null
    mathjax: null
    css: report.css
    includes:
      after_body: report_scroll.html
knit: (function(input, ...) rmarkdown::render(
    input, output_file = "index.html"))
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo      = FALSE,
  message   = FALSE,
  warning   = FALSE,
  fig.width  = 6,
  fig.height = 3.5,
  dpi        = 150,
  out.width  = "100%"
)
library(dplyr)
library(ggplot2)
library(ggridges)

df <- read.csv("../data/talent_market-t3.csv")

temp <- df$salary_usd
temp <- gsub("$", "", temp)
temp <- gsub(",", "", temp)
temp <- gsub("USD", "", temp)
temp <- trimws(temp)
df$salary_usd <- as.numeric(temp)
```

<div class="report-wrap">

<!-- ── HEADER ──────────────────────────────────── -->
<!-- Edit the kicker, headline, deck, and byline.  -->
<!-- Do not change the class names or HTML tags.   -->

<header class="report-header fade-in">
  <p class="report-kicker">
    Data Analysis &middot; MBAA 531
  </p>
  <h1 class="report-headline">
    Your headline goes here
  </h1>
  <p class="report-deck">
    A one or two sentence summary of your argument.
    What does your data reveal? Write this last,
    once you know what the piece says.
  </p>
  <p class="report-byline">
    By <strong>Your Name</strong> &middot;
    Dataset: Your Dataset Name
  </p>
</header>


<!-- ── SECTION 1: THE DATA ─────────────────────── -->

::: {.report-section .fade-in}

## The Data

Write two or three paragraphs here introducing your
dataset. Draw from your Test 2 Section 1 write-up.
Answer: what does this dataset measure, how many
observations does it have, and why does it matter?
Write for a reader who has never seen the data.

:::


<!-- ── SECTION 2: THE CENTRAL FINDING ─────────── -->

::: {.report-section .fade-in}

## The Central Finding

Introduce the derived variable you created in
Test 2 Section 4. Explain what it measures and why
it matters. Then the pull stat block below presents
the summary statistic at a glance.

<!-- Edit the number and label text only.          -->
<!-- Do not change the class names or HTML tags.   -->

<div class="pull-stat fade-in">
  <span class="stat-number">0.00</span>
  <span class="stat-label">
    Replace with your statistic and a one-line
    explanation of what it means in plain language.
  </span>
</div>

Continue the narrative here. What does this number
reveal? Name the variable, the unit of measurement,
and what a high or low value means in context.

:::


<!-- ── SECTION 3: SCATTER CHART ───────────────── -->

::: {.report-section .fade-in}

## A Closer Look

Write one paragraph before the chart that tells the
reader what to look for. Set up the expectation
first, then let the chart confirm or complicate
it. Draw from your Test 3 Chart 2 interpretation.

<div class="chart-wrap">

```{r scatter}
# Paste your scatter chart from Test 3 here.
# Replace colA and colB with your column names.
# Keep the theme calls, they match the page style.
ggplot(df, aes(x = salary_usd, y = experience_yrs)) +
  geom_point(
    alpha  = 0.35,
    size   = 1.4,
    colour = "#c0392b"
  ) +
  labs(title = NULL, x = NULL, y = NULL) +
  theme_minimal(base_size = 12) +
  theme(
    panel.grid.minor = element_blank(),
    panel.grid.major = element_line(
      colour = "#eeeeee"
    ),
    axis.text = element_text(colour = "#555")
  )
```

<p class="chart-caption">
  Chart 1: replace with a short description of what
  the chart shows. Include axis names and units.
</p>
</div>

Write one or two sentences after the chart
connecting what the reader just saw to the broader
argument.

:::


<!-- ── SECTION 4: RIDGE CHART ─────────────────── -->

::: {.report-section .fade-in}

## Across Groups

Write one paragraph before the chart. Which grouping
variable did you choose, and what did you expect to
see? Draw from your Test 4 Section 3 justification.

<div class="chart-wrap">

```{r ridge, eval=FALSE}
# Paste your best ridge chart from Test 4 here.
# Replace colX and groupCol with your column names.
ggplot(df, aes(x    = colX,
               y    = groupCol,
               fill = groupCol)) +
  geom_density_ridges(
    alpha     = 0.55,
    colour    = "white",
    linewidth = 0.4
  ) +
  scale_fill_manual(
    values = rep("#c0392b", 20)
  ) +
  labs(title = NULL, x = NULL, y = NULL) +
  theme_minimal(base_size = 12) +
  theme(
    legend.position    = "none",
    panel.grid.minor   = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.major.x = element_line(
      colour = "#eeeeee"
    ),
    axis.text = element_text(colour = "#555")
  )
```

<p class="chart-caption">
  Chart 2: replace with a short description.
  Name the grouping variable and the continuous
  variable on the x-axis.
</p>
</div>

Write two or three sentences interpreting the chart.
Which groups stand out? What does this reveal that
the scatter chart did not?

:::


<!-- ── CONCLUSION ──────────────────────────────── -->

::: {.report-section .fade-in}

## What This Means

Write two or three paragraphs closing the piece.
Return to the headline claim and show how the two
charts together support it. What would you want a
decision-maker to take away? What question does the
data leave unanswered?

:::


<!-- ── FOOTER ──────────────────────────────────── -->

<footer class="report-footer">
  <p>
    Published via GitHub Pages &middot;
    MBAA 531 Data Analytics &middot;
    Vancouver Island University
  </p>
  <p>
    Source:
    <a href="https://github.com/yourusername/mbaa531-report">
      github.com/yourusername/mbaa531-report
    </a>
  </p>
</footer>

</div><!-- end .report-wrap -->
